\documentclass[11pt]{article}

% NOTE: The "Edit" sections are changed for each assignment

% Edit these commands for each assignment

\newcommand{\assignmentduedate}{April 14}
\newcommand{\assignmentassignedate}{April 7}
\newcommand{\assignmentnumber}{Seven}

\newcommand{\labyear}{2020}
\newcommand{\labdueday}{Tuesday}
\newcommand{\labassignday}{Tuesday}
\newcommand{\labtime}{1:30 pm}

% \newcommand{\assigneddate}{Assigned: \labassignday, \assignmentassignedate, \labyear{} at \labtime{}}
\newcommand{\assigneddate}{Assigned: \labassignday, \assignmentassignedate, \labyear{}}
\newcommand{\duedate}{Due: \labdueday, \assignmentduedate, \labyear{}}

% Edit these commands to give the name to the main program

\newcommand{\mainprogram}{\lstinline{compute_tf_objectoriented.py}}
\newcommand{\mainprogramsource}{\lstinline{termfrequency/compute_tf_objectoriented.py}}

\newcommand{\testprogram}{\lstinline{test_compute_tf_objectoriented.py}}
\newcommand{\testprogramsource}{\lstinline{tests/test_compute_tf_objectoriented.py}}

% Edit this commands to describe key deliverables

\newcommand{\reflection}{\lstinline{writing/reflection.md}}

% Commands to describe key development tasks

% --> Running gatorgrader.sh
\newcommand{\gatorgraderstart}{\command{gradle grade}}
\newcommand{\gatorgradercheck}{\command{gradle grade}}

% --> Compiling and running program with gradle
\newcommand{\gradlebuild}{\command{gradle build}}
\newcommand{\gradlerun}{\command{gradle run}}

% Commands to describe key git tasks

% NOTE: Could be improved, problems due to nesting

\newcommand{\gitcommitfile}[1]{\command{git commit #1}}
\newcommand{\gitaddfile}[1]{\command{git add #1}}

\newcommand{\gitadd}{\command{git add}}
\newcommand{\gitcommit}{\command{git commit}}
\newcommand{\gitpush}{\command{git push}}
\newcommand{\gitpull}{\command{git pull}}

\newcommand{\gitcommitmainprogram}{\command{git commit termfrequency/compute_tf_objectoriented.py -m "Descriptive commit message"}}
\newcommand{\gitcommittestprogram}{\command{git commit tests/test_compute_tf_objectoriented.py -m "Descriptive commit message"}}

% Commands for the textbooks, since there are so many

\newcommand{\cooperative}{{\em Cooperative Software Design\/}}
\newcommand{\philosophy}{{\em Philosophy of Software Design\/}}
\newcommand{\thinkpython}{{\em Think Python\/}}
\newcommand{\programmingstyle}{{\em Exercises in Programming Style\/}}
\newcommand{\pytest}{{\em Python Testing with Pytest\/}}

% Use this when displaying a new command

\newcommand{\command}[1]{``\lstinline{#1}''}
\newcommand{\program}[1]{\lstinline{#1}}
\newcommand{\url}[1]{\lstinline{#1}}
\newcommand{\channel}[1]{\lstinline{#1}}
\newcommand{\option}[1]{``{#1}''}
\newcommand{\step}[1]{``{#1}''}

\usepackage{pifont}
\newcommand{\checkmark}{\ding{51}}
\newcommand{\naughtmark}{\ding{55}}

\usepackage{listings}
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}

\usepackage{fancyhdr}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}

\fancyhf{}
\rhead{Computer Science 203}
\lhead{Practical Assignment \assignmentnumber{}}
\rfoot{Page \thepage}
\lfoot{\duedate}

\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\labtitle}[1]
{
  \begin{center}
    \begin{center}
      \bf
      CMPSC 203\\Software Engineering\\
      Spring 2020\\
      \medskip
    \end{center}
    \bf
    #1
  \end{center}
}

\begin{document}

\thispagestyle{empty}

\labtitle{Practical \assignmentnumber{} \\ \assigneddate{} \\ \duedate{}}

\section*{Objectives}

To practice using GitHub to access the files for a practical assignment.
Additionally, to practice using your laptop's operating system and software
development programs such as a ``terminal window'' and a ``testing tool''. You
will also continue to practice using Slack to support communication with the
technical leaders and the course instructor. You will carry on with practice
in implementing and running a Python program and also using Pipenv and the
course's automated grading tool to assess your progress towards correctly
completing the project. Along with practicing how to use Pytest plugins, you
will refactor the source code of a Python program implemented in the
object-oriented style and then use parameterized testing to establish a
confidence in the program's correctness. You will also further practice the
refactoring of a Python program that does not meet certain design and
implementation standards. Finally, you will compare and contrast the past four
programming styles, identifying your preferences and the trade-offs inherent in
each style.

\section*{Suggestions for Success}

\begin{itemize}
  \setlength{\itemsep}{0pt}

\item {\bf Follow each step carefully}. Slowly read each sentence in the
  assignment sheet, making sure that you precisely follow each instruction.
  Take notes about each step that you attempt, recording your questions and
  ideas and the challenges that you faced. If you are stuck, then please tell a
  technical leader or instructor what assignment step you recently completed.

\item {\bf Regularly ask and answer questions}. Please log into Slack at the
  start of a laboratory or practical session and then join the appropriate
  channel. If you have a question about one of the steps in an assignment, then
  you can post it to the designated channel. Or, you can ask a student sitting
  next to you or talk with a technical leader or the course instructor.

\item {\bf Store your files in GitHub}. As in all of your past assignments, you
  will be responsible for storing all of your files (e.g., Python source code and
  Markdown-based writing) in a Git repository using GitHub Classroom. Please
  verify that you have saved your source code in your Git repository by using
  \command{git status} to ensure that everything is updated. You can see if
  your assignment submission meets the established correctness requirements by
  using the provided checking tools on your local computer and in checking the
  commits in GitHub.

% \item {\bf Keep all of your files}. Don't delete your programs, output files,
%   and written reports after you submit them through GitHub; you will need them
%   again when you study for the quizzes and examinations and work on the other
%   laboratory, practical, and final project assignments.

\item {\bf Back up your files regularly}. All of your files are regularly
  backed-up to the servers in the Department of Computer Science and, if you
  commit your files regularly, stored on GitHub. However, you may want to use a
  flash drive, Google Drive, or your favorite backup method to keep an extra
  copy of your files on reserve. In the event of any type of system failure,
  you are responsible for ensuring that you have access to a recent backup copy
  of all your files.

\item {\bf Explore teamwork and technologies}. While certain aspects of these
  assignments will be challenging for you, each part is designed to give you the
  opportunity to learn both fundamental concepts in the field of computer
  science and explore advanced technologies that are commonly employed at a wide
  variety of companies. To explore and develop new ideas, you should regularly
  communicate with your team and/or the technical leaders and tutors.

\item {\bf Hone your technical writing skills}. Computer science assignments
  require to you write technical documentation and descriptions of your
  experiences when completing each task. Take extra care to ensure that your
  writing is interesting and both grammatically and technically correct,
  remembering that computer scientists must effectively communicate and
  collaborate with their team members and the tutors, technical leaders, and
  course instructor.

\end{itemize}

\section*{Reading Assignment}

If you have not done so already, please read all of the relevant ``GitHub
Guides'', available at \url{https://guides.github.com/}, that explain how to use
many of the features that GitHub provides. In particular, please make sure that
you have read guides such as ``Mastering Markdown'' and ``Documenting Your
Projects on GitHub''; each of them will help you to understand how to use both
GitHub and GitHub Classroom. To do well on this assignment, you should also read
Chapters 1 through 5 in {\em Think Python\/} and the Preface and Chapters 10
through 15 in the {\em Exercises in Programming Style\/}.
%
You should also read the first four chapters in \pytest, making sure that you
understand parameterized testing.
%
Please make sure that you review the relevant content in \cooperative~and
\philosophy.
%
You are also expected to find and read all of the online resources that you need
to complete this assignment.

\section*{Refactoring and Testing an Object-Oriented Python Program}

To access the practical assignment, you should go into the
\channel{\#announcements} channel in our Slack team and find the announcement
that provides a link for it. Copy this link and paste it into your web browser.
Now, you should accept the practical assignment and see that GitHub Classroom
created a new GitHub repository for you to access the assignment's starting
materials and to store the completed version of your assignment. Specifically,
to access your new GitHub repository for this assignment, please click the green
``Accept'' button and then click the link that is prefaced with the label ``Your
assignment has been created here''. If you accepted the assignment and correctly
followed these steps, you should have created a GitHub repository with a name
like
``Allegheny-Computer-Science-203-Spring-2020/computer-science-203-spring-2020-practical-7-gkapfham''.
Unless you provide the instructor with documentation of the extenuating
circumstances that you are facing, not accepting the assignment means that you
automatically receive a failing grade for it.

Study the provided source code and the technical documentation to understand the
type of output that your program produces.
%
Make sure that you notice that this source code is incorrectly formatted and
written in a fashion that uses non-standard features of the Python programming
language.
%
Part of your job for this assignment is to refactor the source code so that it
meets all of the well-established standards for Python programs.
%
Make sure that you format all of the Python source code and its comments so that
it adheres to all of the linting standards, only disabling certain checks when
there is no other alternative.
%
Figures~\ref{fig:data} and~\ref{fig:main} provide two segments of Python source
code that illustrate the correct way to reformat the code, adding the
``pragmas'' that disable certain linting checks as needed.
%
You also need to ensure that the function comments adhere to the standard which
mandates, among other requirements, that there be no spacing in the docstrings
that must end with a period.
%
Students who have questions about how to reformat the source code should talk to
a technical leader or the course instructor, highlighting the problematic
linting check.

As you are improving all of the provided code, you should also run the Pytest
test suite that currently contains one test. Following the strategy of this test
and the documentation for the functions in the program, add all of the test
cases that you would need to achieve high coverage of the program under test.
%
You should also write parameterized Pytest test cases that exercise the
functions in this object-oriented-style program with numerous inputs. To
implement a parameterized test case, you must decorate a Python testing function
with the \command{@pytest.mark.parametrize} annotation.
%
Although you are not required to write all of your tests in a parameterized
fashion, at least some of the new tests that you write must adopt this approach.
%
Whenever possible, you should also use the Hypothesis automated test data
generation tool to automatically create inputs for your test cases, documenting
how the tool enables to you cover the source code of the functions.

Finally, please compare and contrast the pipeline and object-oriented versions
of this program to this one that is written in an object-oriented fashion. What
are the similarities and differences? Which one do you prefer? Which one is
easier to test?
%
Please see the instructor if you have questions about how to refactor the
program's source code to meet set requirements, how to write and run
parameterized tests, or why the object-oriented system is designed in this way.

\begin{figure}[t]
%
\begin{verbatim}
class DataStorageManager(TFExercise):
    """Model the contents of the file."""

    def __init__(self, path_to_file):
        """Define the constructor for the DataStorageManager."""
        with open(path_to_file) as f:
            self._data = f.read()
        pattern = re.compile(r"[\W_]+")
        self._data = pattern.sub(" ", self._data).lower()

    def words(self):
        """Return the list of words in storage."""
        return self._data.split()
\end{verbatim}
%
\vspace*{-.15in}
%
\caption{A Correctly Formatted Class in the {\tt compute\_tf\_objectoriented} Python Program.}\label{fig:data}
%
\vspace*{-.1in}
%
\end{figure}

\section*{Checking the Correctness of Your Program and Writing}

In addition to using your own automated Pytest-based tests, you can use
GatorGrader to check other characteristics of your project. To automatically
check your Python source code you can get started with the use of the
GatorGrader tool, typing the command \gatorgraderstart{} in your terminal
window.
%
Once your program is running correctly, fulfilling at least some of the
assignment's requirements, you should transfer your files to GitHub using the
\gitcommit{} and \gitpush{} commands. For example, if you want to signal that
the \testprogramsource{} file has been changed and is ready for transfer to
GitHub you would first type \gitcommittestprogram{} in your terminal, followed
by typing \gitpush{} and checking to see that the transfer to GitHub is
successful.

After the course instructor enables \step{continuous integration} with a system
called Travis CI, when you use the \gitpush{} command to transfer your source
code to your GitHub repository, Travis CI will initialize a \step{build} of your
assignment, checking to see if it meets all of the requirements. If both your
source code and writing meet all of the established requirements, then you will
see a green \checkmark{} in the listing of commits in GitHub after awhile. If
your submission does not meet the requirements, a red \naughtmark{} will appear
instead. The instructor will reduce a student's grade for this assignment if the
red \naughtmark{} appears on the last commit in GitHub immediately before the
assignment's due date. Yet, if the green \checkmark{} appears on the last commit
in your GitHub repository, then you satisfied all of the main checks and you
will earn full credit. Unless you provide the course instructor with
documentation of the severe and extenuating circumstances that you are facing,
no late work will be considered towards your completion grade for this practical
assignment.

\begin{figure}[t]
%
\begin{verbatim}
class WordFrequencyController(TFExercise):
    """Control the process of collecting word frequency data."""

    def __init__(self, path_to_file):
        """Define the constructor for the WordFrequencyManager."""
        self._storage_manager = DataStorageManager(path_to_file)
        self._stop_word_manager = StopWordManager()
        self._word_freq_manager = WordFrequencyManager()

    def run(self):
        """Run the process of collecting word frequency data."""
        for w in self._storage_manager.words():
            if not self._stop_word_manager.is_stop_word(w):
                self._word_freq_manager.increment_count(w)
        word_freqs = self._word_freq_manager.sorted()
        for (w, c) in word_freqs[0:25]:
            print(w, " - ", c)
\end{verbatim}
%
\vspace*{-.15in}
%
\caption{The Controller Class in the {\tt compute\_tf\_objectoriented} Python Program.}\label{fig:main}
%
\vspace*{-.1in}
%
\end{figure}

\section*{Summary of the Required Deliverables}

\noindent Students do not need to submit printed source code or technical
writing for any assignment in this course. Instead, this assignment invites you
to submit, using GitHub, the following deliverables.

\vspace*{-.25em}

\begin{enumerate}

\setlength{\itemsep}{0in}

\item A documented, well-formated, and correct version of \testprogramsource{}
  that contains at least five passing tests and produces the desired output.
  Make sure that some of the tests adhere to the parameterized testing approach
  supported by Pytest.

\item A revised version of \mainprogramsource{} that, when appropriate, contains
  refactored source code that avoids all of the deprecated features of the
  Python language and is in adherence to the established standard for writing
  Python code.

\item Stored in a Markdown file called \reflection{}, a multi-paragraph
  response, with each paragraph consisting of at least 100 words, for each of
  the prompts. This file should also feature a fenced code block that furnishes
  the output from running the Pytest test suite.

\end{enumerate}

\vspace*{-1em}

\section*{Evaluation of Your Practical Assignment}

Using a report that the instructor shares with you through the commit log in
GitHub, you will privately received a grade on this assignment and feedback on
your submitted deliverables. Your grade for the assignment will be a function of
the whether or not it was submitted in a timely fashion and if your program
received a green \checkmark{} indicating that it met all of the requirements.
Other factors will also influence your final grade on the assignment. In
addition to studying the efficiency and effectiveness and documentation of your
Python source code, the instructor will also evaluate the correctness of your
technical writing. If your submission receives a red \naughtmark{}, the
instructor will reduce your grade for the assignment. Please remember to read
your GitHub repository's \program{README.md} file for a description of the four
grades that you will receive for this practical assignment. Students should
follow the instructions in the \program{README.md} file to ask the instructor to
review their assignment and to provide you with constructive feedback before you
submit it for the final assessment.

\end{document}
