\documentclass[11pt]{article}

% NOTE: The "Edit" sections are changed for each assignment

% Edit these commands for each assignment

\newcommand{\assignmentduedate}{March 13}
\newcommand{\assignmentassignedate}{February 4}
\newcommand{\assignmentnumber}{One}

\newcommand{\labassignmentnumberstart}{Three}
\newcommand{\labassignmentnumberend}{Eight}

\newcommand{\labyear}{2020}
\newcommand{\labdueday}{Friday}
\newcommand{\labassignday}{Tuesday}
\newcommand{\labtime}{2:30 pm}

\newcommand{\assigneddate}{Assigned: \labassignday, \assignmentassignedate, \labyear{} at \labtime{}}
\newcommand{\duedate}{Due: \labdueday, \assignmentduedate, \labyear{} at \labtime{}}

% NOTE: there was no source code for this assignment
% Instead, the focus was on two Markdown files

\newcommand{\assessment}{\lstinline{assessment.md}}
\newcommand{\conduct}{\lstinline{conduct.md}}

% Edit these commands to give the name to the main program

\newcommand{\mainprogram}{\lstinline{compute_tf_monolith.py}}
\newcommand{\mainprogramsource}{\lstinline{src/termfrequency/compute_tf_monolith.py}}

% Edit this commands to describe key deliverables

\newcommand{\reflection}{\lstinline{report.md}}

% Commands to describe key development tasks

% --> Running gatorgrader.sh
\newcommand{\gatorgraderstart}{\command{gradle grade}}
\newcommand{\gatorgradercheck}{\command{gradle grade}}

% --> Compiling and running program with gradle
\newcommand{\gradlebuild}{\command{gradle build}}
\newcommand{\gradlerun}{\command{gradle run}}

% Commands to describe key git tasks

% NOTE: Could be improved, problems due to nesting

\newcommand{\gitcommitfile}[1]{\command{git commit #1}}
\newcommand{\gitaddfile}[1]{\command{git add #1}}

\newcommand{\gitadd}{\command{git add}}
\newcommand{\gitcommit}{\command{git commit}}
\newcommand{\gitpush}{\command{git push}}
\newcommand{\gitpull}{\command{git pull}}

\newcommand{\gitcommitmainprogram}{\command{git commit src/termfrequency/compute_tf_monolith.py -m "Descriptive commit message"}}

% Commands for the textbooks, since there are so many

\newcommand{\cooperative}{{\em Cooperative Software Design\/}}
\newcommand{\philosophy}{{\em Philosophy of Software Design\/}}
\newcommand{\thinkpython}{{\em Think Python\/}}
\newcommand{\programmingstyle}{{\em Exercises in Programming Style\/}}
\newcommand{\pytest}{{\em Python Testing with Pytest\/}}

% Use this when displaying a new command

\newcommand{\command}[1]{``\lstinline{#1}''}
\newcommand{\program}[1]{\lstinline{#1}}
\newcommand{\url}[1]{\lstinline{#1}}
\newcommand{\channel}[1]{\lstinline{#1}}
\newcommand{\option}[1]{``{#1}''}
\newcommand{\step}[1]{``{#1}''}

\usepackage{pifont}
\newcommand{\checkmark}{\ding{51}}
\newcommand{\naughtmark}{\ding{55}}

\usepackage{listings}
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}

\usepackage{fancyhdr}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}

\fancyhf{}
\rhead{Computer Science 203}

\lhead{Software Project \assignmentnumber{} (Laboratory Assignments \labassignmentnumberstart{} through \labassignmentnumberend{})}

\rfoot{Page \thepage}
\lfoot{\duedate}

\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\labtitle}[1]
{
  \begin{center}
    \begin{center}
      \bf
      CMPSC 203\\Software Engineering\\
      Spring 2020\\
      \medskip
    \end{center}
    \bf
    #1
  \end{center}
}

\begin{document}

\thispagestyle{empty}

\labtitle{Software Project \assignmentnumber{} \\ Laboratory Assignments \labassignmentnumberstart{} through \labassignmentnumberend{} \\ \assigneddate{} \\ \duedate{}}

\section*{Objectives}

To use GitHub and the GitHub flow model to collaboratively engineer, deliver,
and evaluate a software product.
%
Along with using GitHub features like the issue tracker and reviewing pull
requests, in this assignment you will use Markdown to complete technical writing
tasks and the Python programming language and many Python packages (e.g., Pytest
for automated testing) to implement a production quality program.
%
As a side effect of working in a team, you will also experience challenges, such
as the creation of merge conflicts in a version control repository, that force
you to develop practical solutions.
%
You will also gain experience in talking with team members and leaders,
technical leaders, and the course instructor.
%
Students will work together in a development team while mastering the technical
and professional skills in the field of software engineering, completing a
weekly assessment of their progress.
%
Students will also adhere to a code of conduct that governs how all team members
will interact during the completion of software products.
%
Students will regularly receive both percentage and mastery grades on this
project.

\section*{Suggestions for Success}

\begin{itemize}
  \setlength{\itemsep}{0pt}

\item {\bf Follow each step carefully}. Slowly read each sentence in the
  assignment sheet, making sure that you precisely follow each instruction. Take
  notes about each step that you attempt, recording your questions and ideas and
  the challenges that you faced. If you are stuck, then please tell a technical
  leader or instructor what assignment step you recently completed.

\item {\bf Regularly ask and answer questions}. Please log into Slack at the
  start of a laboratory or practical session and then join the appropriate
  channel. If you have a question about one of the steps in an assignment, then
  you can post it to the designated channel. Or, you can ask a student sitting
  next to you or talk with a technical leader or the course instructor.

\item {\bf Store your files in GitHub}. Starting with this laboratory
  assignment, you will be responsible for storing all of your files (e.g., Java
  source code and Markdown-based writing) in a Git repository using GitHub
  Classroom. Please verify that you have saved your source code in your Git
  repository by using \command{git status} to ensure that everything is
  updated. You can see if your assignment submission meets the established
  correctness requirements by using the provided checking tools on your local
  computer and by checking the commits in GitHub.

\item {\bf Keep all of your files}. Don't delete your programs, output files,
  and written reports after you submit them through GitHub; you will need them
  again when you study for the quizzes and examinations and work on the other
  laboratory, practical, and final project assignments.

\item {\bf Explore teamwork and technologies}. While certain aspects of the
  laboratory assignments will be challenging for you, each part is designed to
  give you the opportunity to learn both fundamental concepts in the field of
  computer science and explore advanced technologies that are commonly employed
  at a wide variety of companies. To explore and develop new ideas, you should
  regularly communicate with your team and/or the student technical leaders.

\item {\bf Hone your technical writing skills}. Computer science assignments
  require to you write technical documentation and descriptions of your
  experiences when completing each task. Take extra care to ensure that your
  writing is interesting and both grammatically and technically correct,
  remembering that computer scientists must effectively communicate and
  collaborate with their team members and the student technical leaders and
  course instructor.

\item {\bf Review the Honor Code on the syllabus}. While you may discuss your
  assignments with others, copying source code or writing is a violation of
  Allegheny College's Honor Code.

\end{itemize}

\section*{Reading Assignment}

% Course Textbooks:

% Cooperative Software Design
% Philosophy of Software Design
% Think Python
% Exercises in Programming Style
% Python Testing with Pytest

If you have not done so already, please read all of the relevant ``GitHub
Guides'', available at \url{https://guides.github.com/}, that explain how to use
many of the features that GitHub provides. In particular, please make sure that
you have read guides such as ``Mastering Markdown'' and ``Documenting Your
Projects on GitHub''; each of them will help you to understand how to use both
GitHub and GitHub Classroom.
%
To do well on this assignment you should also read all of the assigned chapters
in the following textbooks: \cooperative, \philosophy, \thinkpython,
\programmingstyle, and \pytest.
%
You are also expected to find and read all of the online resources that you need
to complete this software project.
%
Please see the course instructor if you have questions on these reading
assignments.

\section*{Developing and Releasing the Cogitate Tool for Repository Insights}

% Accept the assignment

To access this laboratory assignment, you should go into the
\channel{\#announcements} channel in our Slack team and find the announcement
that provides a link for it. Copy this link and paste it into your web browser.
Now, you should accept the laboratory assignment and see that GitHub Classroom
created a new GitHub repository for you to access the assignment's starting
materials and to store the completed version of your assignment. Specifically,
to access your new GitHub repository for this assignment, please click the green
``Accept'' button and then click the link that is prefaced with the label ``Your
assignment has been created here''. If you accepted the assignment and correctly
followed these steps, you should have created a GitHub repository with a name
like
``Allegheny-Computer-Science-203-Spring-2020/computer-science-203-spring-2020-lab-2-gkapfham''.
Unless you provide the instructor with documentation of the extenuating
circumstances that you are facing, not accepting the assignment means that you
will receive a failing grade for it.
%
Instead of giving you access to ``starter'' code for this assignment, the
purpose of this GitHub repository is to facilitate the assessment of your own
mastery of the professional and technical skills in software engineering and to
attest to the fact that you adhered to the course's code of conduct.
%
Please note that you will complete these steps during every week of the project.

% Details of what students must complete

Unlike the practical assignments, this laboratory assignment asks you to work in
a entire-class team to create and release a software product.
%
For this laboratory assignment, your task is to collaborate with the members of
your class to design, implement, test, deploy, and maintain a tool, called
Cogitate, that can analyze a GitHub repository and surface insights about how
well individuals and groups of team members collaborated to engineer a software
system. Upon completion of Cogitate, the course instructor will use it to
evaluate how well individuals and groups made contributions to this software
project. The course instructor will also use Cogitate to evaluate how well teams
collaborate in his other courses, with the ultimate goal of seeing Cogitate
deployed widely for use in the Department of Computer Science during the
upcoming academic year.

\vspace*{-.5em}

\begin{itemize}

  \setlength{\itemsep}{0pt}

  \item How many commits did an individual make to a GitHub repository?

  \item How many lines of code did an individual add, modify, and delete?

  \item Why types of files did an individual normally modify in a repository?

  \item What is the overall score for an individual's contribution to a team
    project?

  \item Are there individuals who collaborate together too frequently or not
    enough?

  \item Are there team members who are ``code hoarders'' or ``domain
    experts''?

  \item Are there team members who contribute source code without also added
    test cases?

  \item Are there team members who break the build or contribute to unusually
    high code churn?

  \item Are there team members who frequently fix the build right before merging
    a PR to master?

  \item Are there team members who are unable to contribute or who seem stuck on
    finishing a task?

\end{itemize}

\vspace*{-.5em}

Since this assignment's goal is for all students to work together to finish a
production quality version of Cogitate, the tasks for this project are not
limited to those that are currently in the issue tracker. That is, everyone is
responsible for working together to handle these issues and any others that
arise during the completion of this long-term software project.

\section*{Collaborating with Your Software Engineering Team}

Your team should use GitHub and its features (e.g., issue tracker, pull
requests, commit log, and code review request) to complete all of the tasks
referenced in the previous section.
%
Aiming to manage risk and estimate the effort required for individual team
members to complete this project, you should assign people to teams, roles, and
tasks. While it is acceptable for you to have in-person discussions with your
team members or to talk about the project through Slack, please remember that
all important discussions and decisions must be documented through GitHub.
Finally, as you are working with your team, you should carefully document your
experiences and contributions so that you can share them through writing stored
in the repository created by GitHub Classroom.

Since multiple approaches may support the effective completion of the required
software, this assignment does not dictate team organization or communication
strategies. The students in the course should instead work with each other, the
technical leads, and the course instructor to identify team roles and strategies
for effective organization and communication. With that said, you should plan to
use either forks or branches of a GitHub repository to organize your work.
%
Once a specific branch/fork contains the finished version of its associated
deliverable, a team member should create a pull request for discussion and
review. If the team leaders, the technical leaders, and the course instructor
judge that the pull request has all of the expected characteristics, then it
should be merged into the ``master'' branch of the appropriate repository. If
the pull request is not accepted, then team member(s) should improve it until it
meets every reviewer's expectations. Your team should continue to use this
model, called ``GitHub Flow'', to support the completion of all deliverables.
%
Students with questions about the use of GitHub should first talk to a team
leader.

\section*{Skill Assessment and Code of Conduct}

% Ratings and code of conduct

Your GitHub repository for each week will contain versions of the assessment
sheet and code of conduct that we jointly created at the start of the semester.
Please copy those files into your repository and complete them fully. For each
week of this project you should describe your efforts on this software project
according to the following levels: N = None, I = Inadequate, A = Adequate, G =
Good, and E = Excellent. Your evaluation of your own work should focus on your
mastery of both technical and professional skills in software engineering. You
should thoughtfully reflect on your current areas of expertise and opportunities
for improvement. By the mid-way and end points of this project, you should have
demonstrated mastery of at least half and all the skills in the assessment
sheet, respectively. You should also use the skill assessment sheet to document
the work that you completed for this project. As you work on this project, you
must be proactive in finding ways to master all of the listed skills. Finally,
you should ``sign'' your name in the code of conduct to indicate that you
adhered to it throughout the completion of the software project.

% Checking of the assessment sheet and the code of conduct guide

Please remember that Travis CI is configured to use \command{mdl} and/or
GatorGrader to check the Markdown files in your repository created by GitHub
Classroom.
%
If you saved the files correctly and your writing meets all of the requirements
set by these linting tools, then you will see a green \checkmark{} in the
listing of commits in GitHub after awhile. If your submission does not meet the
requirements, a red \naughtmark{} will appear instead. The instructor will
reduce a student's grade for this assignment if the red \naughtmark{} appears on
the last commit in GitHub immediately before the assignment's due date. Yet, if
the green \checkmark{} appears on the last commit in your GitHub repository,
then you satisfied the basic linting checks for the Markdown files that contain
the assessment sheet and the code of conduct.

\section*{Suggested Schedule for the Software Engineering Project}

The course instructor invites the students in this class to work together to
devise a schedule by which they can complete the software product by the stated
deadline. Overall, you will work on this assignment for six weeks. Here is a
suggestion for a schedule to complete Cogitate:

\begin{itemize}

  \setlength{\itemsep}{0pt}

  \item {\bf Week One}: After learning how to use the some of the suggested
    tools for building Cogitate, create a GitHub repository, raise issues in
    GitHub, form your teams, and assign tasks.

  \item {\bf Week Two}: Once you have finished, for instance, organizing your
    team, and raising issues in GitHub, explore the Python language features and
    packages you will need to implement your features. Start implementing a
    basic prototype of Cogitate for your assigned features.

  \item {\bf Week Three}: Finish implementing prototype features and give a
    demonstration to people who will use your tool, requesting feedback that you
    incorporate into subsequent versions.

  % \item {\bf Week Four}: Implement more features and finish defect fixes,
  %   ultimately leading to a full-featured demonstration that leads to more
  %   feedback from people who use the tool.

  \item {\bf Week Four}: While continuing to incrementally enhance the tool,
    release a completed version so that external individuals can use it and
    provide detailed feedback through the issue tracker.

  \item {\bf Week Five}: Implement all key features and complete all major
    fixes, ultimately leading to a full-featured demonstration and further
    feedback from more people who use the tool.

  \item {\bf Week Six}: Release a production quality tool suitable for use by
    others and by the course instructor, who will use it to create assess each
    person's contribution to this software project.

  % \item {\bf Week Six}: Release a production quality tool suitable for use by
  %   others and by the course instructor, who will use it to create student teams
  %   for the upcoming course assignments.

  % \item {\bf Week Seven}: Release a production quality tool suitable for use by
  %   others and by the course instructor, who will use it to create student teams
  %   for the upcoming course assignments.

\end{itemize}

\noindent You will receive a percentage grade for your cumulative work on weeks
three and six; the interim work will be assessed on a completion basis. Please
see the instructor with your grading questions.

\section*{Summary of the Required Deliverables}

\noindent Students do not need to submit printed source code or technical
writing for any assignment in this course. Instead, this assignment invites you
to submit, using GitHub, the following deliverables. Depending on the week, your
work will be graded on a either a letter or a checkmark basis.
%
Unless you provide the instructor with documentation of the severe and
extenuating circumstances that you are facing, no late work will be considered
towards your grades for this software project.

\begin{enumerate}

\setlength{\itemsep}{0in}

\item A properly documented, well-formatted, and (sometimes partially) completed
  version of \assessment{} that meets all of the established requirements and
  includes an assessment of a student's mastery of professional and technical
  skills in the field of software engineering.

\item A properly documented, well-formatted, and completed version of \conduct{}
  containing a full code of conduct and a statement that the student adhered to
  it during this project.

\item Available for download from a GitHub repository that you team creates, a
  finished, high-quality tool for Git repository analysis that is written in
  Python and in production use.

\end{enumerate}

\end{document}
