\documentclass[11pt]{article}

% NOTE: The "Edit" sections are changed for each assignment

% Edit these commands for each assignment

\newcommand{\assignmentduedate}{March 4}
\newcommand{\assignmentassignedate}{February 28}
\newcommand{\assignmentnumber}{Six}

\newcommand{\labyear}{2020}
\newcommand{\labdueday}{Wednesday}
\newcommand{\labassignday}{Friday}
\newcommand{\labtime}{1:30 pm}

\newcommand{\assigneddate}{Assigned: \labassignday, \assignmentassignedate, \labyear{} at \labtime{}}
\newcommand{\duedate}{Due: \labdueday, \assignmentduedate, \labyear{} at \labtime{}}

% Edit these commands to give the name to the main program

\newcommand{\mainprogram}{\lstinline{compute_tf_pipeline.py}}
\newcommand{\mainprogramsource}{\lstinline{termfrequency/compute_tf_pipeline.py}}

\newcommand{\testprogram}{\lstinline{test_compute_tf_pipeline.py}}
\newcommand{\testprogramsource}{\lstinline{tests/test_compute_tf_pipeline.py}}

% Edit this commands to describe key deliverables

\newcommand{\reflection}{\lstinline{writing/reflection.md}}

% Commands to describe key development tasks

% --> Running gatorgrader.sh
\newcommand{\gatorgraderstart}{\command{gradle grade}}
\newcommand{\gatorgradercheck}{\command{gradle grade}}

% --> Compiling and running program with gradle
\newcommand{\gradlebuild}{\command{gradle build}}
\newcommand{\gradlerun}{\command{gradle run}}

% Commands to describe key git tasks

% NOTE: Could be improved, problems due to nesting

\newcommand{\gitcommitfile}[1]{\command{git commit #1}}
\newcommand{\gitaddfile}[1]{\command{git add #1}}

\newcommand{\gitadd}{\command{git add}}
\newcommand{\gitcommit}{\command{git commit}}
\newcommand{\gitpush}{\command{git push}}
\newcommand{\gitpull}{\command{git pull}}

\newcommand{\gitcommitmainprogram}{\command{git commit termfrequency/compute_tf_pipline.py -m "Descriptive commit message"}}
\newcommand{\gitcommittestprogram}{\command{git commit tests/test_compute_tf_pipline.py -m "Descriptive commit message"}}

% Commands for the textbooks, since there are so many

\newcommand{\cooperative}{{\em Cooperative Software Design\/}}
\newcommand{\philosophy}{{\em Philosophy of Software Design\/}}
\newcommand{\thinkpython}{{\em Think Python\/}}
\newcommand{\programmingstyle}{{\em Exercises in Programming Style\/}}
\newcommand{\pytest}{{\em Python Testing with Pytest\/}}

% Use this when displaying a new command

\newcommand{\command}[1]{``\lstinline{#1}''}
\newcommand{\program}[1]{\lstinline{#1}}
\newcommand{\url}[1]{\lstinline{#1}}
\newcommand{\channel}[1]{\lstinline{#1}}
\newcommand{\option}[1]{``{#1}''}
\newcommand{\step}[1]{``{#1}''}

\usepackage{pifont}
\newcommand{\checkmark}{\ding{51}}
\newcommand{\naughtmark}{\ding{55}}

\usepackage{listings}
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}

\usepackage{fancyhdr}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}

\fancyhf{}
\rhead{Computer Science 203}
\lhead{Practical Assignment \assignmentnumber{}}
\rfoot{Page \thepage}
\lfoot{\duedate}

\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\labtitle}[1]
{
  \begin{center}
    \begin{center}
      \bf
      CMPSC 203\\Software Engineering\\
      Spring 2020\\
      \medskip
    \end{center}
    \bf
    #1
  \end{center}
}

\begin{document}

\thispagestyle{empty}

\labtitle{Practical \assignmentnumber{} \\ \assigneddate{} \\ \duedate{}}

\section*{Objectives}

To practice using GitHub to access the files for a practical assignment.
Additionally, to practice using the Ubuntu operating system and software
development programs such as a ``terminal window'' and a ``testing tool''. You
will also continue to practice using Slack to support communication with the
teaching assistants and the course instructor. You will carry on with practice
in implementing and running a Python program and also using Pipenv and the
course's automated grading tool to assess your progress towards correctly
completing the project. Along with practicing how to use an automated test data
generation and property-based testing tool, called Hypothesis, you will repair
the code (and GitHub repository) of a Python program implemented in the pipeline
style and then use a diverse test suite to establish a confidence in the
program's correctness.

\section*{Suggestions for Success}

\begin{itemize}
  \setlength{\itemsep}{0pt}

\item {\bf Follow each step carefully}. Slowly read each sentence in the
  assignment sheet, making sure that you precisely follow each instruction. Take
  notes about each step that you attempt, recording your questions and ideas and
  the challenges that you faced. If you are stuck, then please tell a technical
  leader or instructor what assignment step you recently completed.

\item {\bf Regularly ask and answer questions}. Please log into Slack at the
  start of a laboratory or practical session and then join the appropriate
  channel. If you have a question about one of the steps in an assignment, then
  you can post it to the designated channel. Or, you can ask a student sitting
  next to you or talk with a technical leader or the course instructor.

\item {\bf Store your files in GitHub}. Starting with this laboratory
  assignment, you will be responsible for storing all of your files (e.g.,
  Python source code and Markdown-based writing) in a Git repository using
  GitHub Classroom. Please verify that you have saved your source code in your
  Git repository by using \command{git status} to ensure that everything is
  updated. You can see if your assignment submission meets the established
  correctness requirements by using the provided checking tools on your local
  computer and by checking the commits in GitHub.

\item {\bf Keep all of your files}. Don't delete your programs, output files,
  and written reports after you submit them through GitHub; you will need them
  again when you study for the quizzes and examinations and work on the other
  laboratory, practical, and final project assignments.

\item {\bf Explore teamwork and technologies}. While certain aspects of the
  laboratory assignments will be challenging for you, each part is designed to
  give you the opportunity to learn both fundamental concepts in the field of
  computer science and explore advanced technologies that are commonly employed
  at a wide variety of companies. To explore and develop new ideas, you should
  regularly communicate with your team and/or the student technical leaders.

\item {\bf Hone your technical writing skills}. Computer science assignments
  require to you write technical documentation and descriptions of your
  experiences when completing each task. Take extra care to ensure that your
  writing is interesting and both grammatically and technically correct,
  remembering that computer scientists must effectively communicate and
  collaborate with their team members and the student technical leaders and
  course instructor.

\item {\bf Review the Honor Code on the syllabus}. While you may discuss your
  assignments with others, copying source code or writing is a violation of
  Allegheny College's Honor Code.

\end{itemize}

\section*{Reading Assignment}

If you have not done so already, please read all of the relevant ``GitHub
Guides'', available at \url{https://guides.github.com/}, that explain how to use
many of the features that GitHub provides. In particular, please make sure that
you have read guides such as ``Mastering Markdown'' and ``Documenting Your
Projects on GitHub''; each of them will help you to understand how to use both
GitHub and GitHub Classroom. To do well on this assignment, you should also read
Chapters 1 through 5 in {\em Think Python\/} and the Preface and Chapters 1
through 5 in the {\em Exercises in Programming Style\/}.
%
You should also read the first two chapters in \pytest, making sure that you
understand parameterized testing.
%
Please make sure that you review the relevant content in \cooperative~and
\philosophy.
%
You are also expected to find and read all of the online resources that you need
to complete this assignment.
%
Specifically, students should review all of the online documentation and
tutorials about Hypothesis and read the paper about the Hypothesis tool
published in the {\em Journal of Open Source Software}.

\section*{Repairing and Testing a Pipeline-Style Program}

To access the practical assignment, you should go into the
\channel{\#announcements} channel in our Slack team and find the announcement
that provides a link for it. Copy this link and paste it into your web browser.
Now, you should accept the practical assignment and see that GitHub Classroom
created a new GitHub repository for you to access the assignment's starting
materials and to store the completed version of your assignment. Specifically,
to access your new GitHub repository for this assignment, please click the green
``Accept'' button and then click the link that is prefaced with the label ``Your
assignment has been created here''. If you accepted the assignment and correctly
followed these steps, you should have created a GitHub repository with a name
like
``Allegheny-Computer-Science-203-Spring-2020/computer-science-203-spring-2020-practical-6-gkapfham''.
Unless you provide the instructor with documentation of the extenuating
circumstances that you are facing, not accepting the assignment means that you
automatically receive a failing grade for it.

As you start this assignment, make sure that you notice that, while this program
is now correctly formatted and in adherence to best practices for Python
programming, it instead contains more than one defect.
%
Part of your job for this assignment is to identify the defects in the program
to ensure that the provided test suite passes correctly and that the program as
a whole runs correctly.
%
As you are improving all of the provided code, you should also run the Pytest
test suite that contains three different types of tests. Make sure that you
understand how these types of test work and try to implement some of your own
tests that follow these patterns.
%
Since you have already practiced writing single-input tests and parameterized
tests, now you should try to create and run property-based tests that
automatically generate inputs using the Hypothesis tool, as seen in
Figure~\ref{fig:param}.
%
Importantly, the Hypothesis tool can automatically generate inputs to the
function under test, enabling a tester to systematically explore the input space
and increasing the likelihood of finding a defect.
%
As you complete this assignment, make sure that you understand how source code
statements like \command{@given(input_string=text(min_size=1, max_size=100))}
lead to Hypothesis generating many inputs.
%
Please see the instructor if you have questions about either how to repair the
program's source code to to fix the defects or how to write and run
Hypothesis-driven tests.

\begin{figure}[t]

\begin{verbatim}
@given(input_string=text(min_size=1, max_size=100))
@settings(verbosity=Verbosity.verbose, deadline=None)
@pytest.mark.hypothesisworks
def test_filter_normalize_correctly_automated_bounded(input_string):
    filtered_normalized_string = compute_tf_pipeline.filter_chars_and_normalize(
        input_string
    )
    assert isinstance(filtered_normalized_string, str)
    assert len(input_string) >= len(filtered_normalized_string)
    assert isinstance(compute_tf_pipeline.scan(filtered_normalized_string), list)
    for word in compute_tf_pipeline.scan(filtered_normalized_string):
        assert word.isalnum()
        assert not word.isspace()
\end{verbatim}

\vspace*{-.15in}

\caption{A Property-Based Test for {\tt filtered\_normalized\_string} in {\tt compute\_tf\_pipeline}.}\label{fig:param}

\vspace*{-.1in}

\end{figure}

\section*{Checking the Correctness of Your Program and Writing}

In addition to using your own automated Pytest-based tests, you can use
GatorGrader to check other characteristics of your project. To automatically
check your Python source code you can get started with the use of the
GatorGrader tool, typing the command \gatorgraderstart{} in your terminal
window.
%
Once your program is running, fulfilling at least some of the assignment's
requirements, you should transfer your files to GitHub using the \gitcommit{}
and \gitpush{} commands.

% For example, if you want to signal that the \testprogramsource{} file has been
% changed and is ready for transfer to GitHub you would first type
% \gitcommittestprogram{} in your terminal, followed by typing \gitpush{} and
% checking to see that the transfer to GitHub is successful.

% After the course instructor enables \step{continuous integration} with a
% system called Travis CI, when you use the \gitpush{} command to transfer your
% source code to your GitHub repository,

Remember, Travis CI will initialize a \step{build} of your assignment, checking
to see if it meets all of the baseline requirements. If both your source code
and writing meet all of the established requirements, then you will see a green
\checkmark{} in the listing of commits in GitHub after awhile. If your
submission does not meet the requirements, a red \naughtmark{} will appear
instead. The instructor will reduce a student's grade for this assignment if the
red \naughtmark{} appears on the last commit in GitHub immediately before the
assignment's due date. Yet, if the green \checkmark{} appears on the last commit
in your GitHub repository, then you satisfied all of the main checks and you
will earn full credit. Unless you provide the course instructor with
documentation of the severe and extenuating circumstances that you are facing,
no late work will be considered towards your completion grade for this practical
assignment.

\section*{Summary of the Required Deliverables}

\noindent Students do not need to submit printed source code or technical
writing for any assignment in this course. Instead, this assignment invites you
to submit, using GitHub, the following deliverables.

\vspace*{-.25em}

\begin{enumerate}

\setlength{\itemsep}{0in}

\item A properly documented, well-formatted, and correct version of
  \testprogramsource{} that contains only passing tests and produces the
  diagnostic output with Hypothesis.

  % Make sure that some of the tests adhere to the
  % parameterized testing approach supported by Pytest.

\item A revised version of \mainprogramsource{} that, when appropriate, contains
  repaired source code that avoids all of the deprecated features of the Python
  programming language and is in adherence with the established standard for
  writing Python source code.

\item Stored in a Markdown file called \reflection{}, a multiple-paragraph
  response, with each paragraph consisting of at least 100 words, for each of
  the stated prompts. This file should feature fenced code blocks that gives the
  two outputs from running a test suite.

\end{enumerate}

\vspace*{-1em}

\section*{Evaluation of Your Practical Assignment}

Practical assignments are graded on a completion --- or ``checkmark'' --- basis.
If your GitHub repository has a \checkmark{} for the last commit before the
deadline then you will receive the highest possible grade for the assignment.
However, you will fail the assignment if you do not complete it correctly, as
evidenced by a red \naughtmark{} in your commit listing, by the set deadline for
finishing the project.

\end{document}
